Reproductible Research Course  at coursera : First Assigment
========================================================

# Data summary

```{r}
# first we clear everything
rm(list=ls())
#Home dir
setwd("C:/Chris/Gremaq2014/Coursera/RR/progs") 
# My Packages 
library(xtable)
library(KernSmooth)
library(ggplot2)

# Stet global option 
opts_chunk$set(ECHO = TRUE)

``` 
First we read the data
```{r}
data <- read.csv("../Data/activity.csv")

```

The data consists of two months of data from <b> a unique anonymous individual </b> collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day. The data file is named  acitvity.csv and can be downloaded from the coursera Webpage. We have a sample of  <b>`r nrow(data)` </b> observations and <b>`r ncol(data)`</b> variables.

# Data analysis 
The mean total number of steps taken per day is just something we could represent over time but we need to do some calculation first

```{r }
data$date <- as.factor(data$date)
data$steps <- as.numeric(data$steps)


data$total.steps = tapply(data$steps,data$date,sum)  #apply the mean function to count steps  each date
data$unique.date = tapply(data$date,data$date,unique)
attach(data)

```


```{r fig.width=7, fig.height=6}

hist(total.steps, freq=FALSE, nclass=13)
```

On this sample, we observe that the mean total number of steps taken per day is 
<b>`r mean(data$total.steps, na.rm= TRUE)` </b>   ( with the median =  `r median(total.steps,  na.rm= TRUE)`  ).


```{r }
plot(unique.date,total.steps,type= "l",ylab="Total Steps/day")  

```


